\titleformat Exhaustive Search of Binary Code Generator for Solving Non\\Interactive Ulam's Searching Problem with Many Lies

### 2018-08-09 src/tex/paper-isst.tex
fix yg masih b.ind dan citation salah

In the development of information technology over the last few decades, information technology is often used as a solution to the problems that ever existed, which was previously solved manually by humans. Examples of problems that ever existed were one of the classic Ulam and Rényi searching problem. This problem can be illustrated by the presence of two players called questioner and answerer. Given search space $S_M = {0,\ldots,M-1}$, answerer choose a value $x \in S_M$. Questioner must find the value $x$ by asking some yes-no question, is "$x \in Q$?", where $Q \subset S_M$, then answerer answer with "yes" or "no". The main problem is the answerers can lie up $e$ times. The problem with this game is to find the minimum number of queries to be able to determine the value of $x$.

@@

The rule of how the answerers are allowed to lie is the fundamental rule in the Ulam and Rényi search game. The rules of probability lie triggered by Rényi and the lie number rule triggered by Ulam \cite{Ulam1991}. On a globally bounded error probability, the probability of the answerer may lie is $r$, so the answerer may lie up to $rn$ times where $n$ is number of question and $r<1$ \cite{Dhagat1992}. On the rule of how many times the answerer can lie, the amount of answerer can lie vary between only one \cite{Ellis2008} \cite{Pelc1988}, two \cite{Cicalese2000}, three \cite{Negro1992}, and more than three lies \cite{Berlekamp1998} \cite{Deppe2004}.

@@

\begin{figure}
	\centering
	\begin{tikzpicture}
	\begin{axis}[
	xlabel={Jumlah maksimal bohong $e$},
	ylabel={Jumlah query},
	legend pos=north west,
	grid style=dashed,
	legend entries={1,2,3,4,5},
	]
	\addplot[green,mark=*] table{data/brute-min.dat};
	\addplot[red,mark=o] table{data/brute-min-max.dat};
	\addplot[blue,mark=o] table{data/brute-max-min.dat};
	\addplot[purple,mark=*] table{data/brute-min-mincount.dat};
	\addplot[black,mark=o] table{data/brute-repetition.dat};
	\end{axis}
	\end{tikzpicture}
	\caption{Testing of selection function greedy algorithm}
	\label{fig:graph_selection_function}
\end{figure}

\begin{figure}
	\centering
	\begin{tikzpicture}
	\begin{axis}[
	xlabel={Jumlah ruang pencarian($2^m$)},
	ylabel={Waktu eksekusi(detik)},
	legend pos=north west,
	grid style=dashed,
	legend entries={Pengulangan biner,Kode biner,Tabel pencarian},
	]
	\addplot[blue,mark=triangle] table{data/timeR.dat};
	\addplot[red,mark=*] table{data/timeB.dat};
	\addplot[green,mark=square] table{data/timeL.dat};
	\end{axis}
	\end{tikzpicture}
	\caption{Grafik perbandingan waktu eksekusi}
	\label{fig:graph_time}
\end{figure}

\begin{figure}
	\centering
	\begin{tikzpicture}
	\begin{axis}[
	xlabel={Jumlah ruang pencarian($2^m$)},
	ylabel={Penggunaan memory(byte)},
	legend pos=north west,
	grid style=dashed,
	legend entries={Pengulangan biner,Kode biner,Tabel pencarian},
	]
	\addplot[blue,mark=triangle] table{data/memoryR.dat};
	\addplot[red,mark=*] table{data/memoryB.dat};
	\addplot[green,mark=square] table{data/memoryL.dat};
	\end{axis}
	\end{tikzpicture}
	\caption{Grafik perbandingan penggunaan memory}
	\label{fig:graph_memory}
\end{figure}

>>>>

In the development of information technology over the last few decades, information technology is often used as a solution to the problems that ever existed, which was previously solved manually by humans. Examples of problems that ever existed were one of the classic Ulam and Rényi searching problem. This problem can be illustrated by the presence of two players called questioner and answerer. Given search space $S_M = \{0,\ldots,M-1\}$, answerer choose a value $x \in S_M$. Questioner must find the value $x$ by asking some yes-no question, is "$x \in Q$?", where $Q \subset S_M$, then answerer answer with "yes" or "no". The main problem is the answerers can lie up $e$ times. The problem with this game is to find the minimum number of queries to be able to determine the value of $x$.

@@

The rule of how the answerers are allowed to lie is the fundamental rule in the Ulam and Rényi search game. The rules of probability lie triggered by Rényi and the lie number rule triggered by Ulam \cite{StanislawMUlam1976}. On a globally bounded error probability, the probability of the answerer may lie is $r$, so the answerer may lie up to $rn$ times where $n$ is number of question and $r<1$ \cite{Dhagat1999}. On the rule of how many times the answerer can lie, the number of answerer can lie vary between only one \cite{Ellis2008} \cite{Pelc1988}, two \cite{Cicalese2000}, three \cite{Negro1992}, and more than three lies \cite{Berlekamp1998} \cite{Deppe2004}.

@@

\begin{figure}
	\centering
	\begin{tikzpicture}
	\begin{axis}[
	xlabel={Maximal lies $e$},
	ylabel={Number of queries},
	legend pos=north west,
	grid style=dashed,
	legend entries={1,2,3,4,5},
	]
	\addplot[green,mark=*] table{data/brute-min.dat};
	\addplot[red,mark=o] table{data/brute-min-max.dat};
	\addplot[blue,mark=o] table{data/brute-max-min.dat};
	\addplot[purple,mark=*] table{data/brute-min-mincount.dat};
	\addplot[black,mark=o] table{data/brute-repetition.dat};
	\end{axis}
	\end{tikzpicture}
	\caption{Testing of selection function greedy algorithm}
	\label{fig:graph_selection_function}
\end{figure}

\begin{figure}
	\centering
	\begin{tikzpicture}
	\begin{axis}[
	xlabel={Search space ($2^m$)},
	ylabel={Execution time (sec)},
	legend pos=north west,
	grid style=dashed,
	legend entries={Binary repetition,Binary code,Lookup table},
	]
	\addplot[blue,mark=triangle] table{data/timeR.dat};
	\addplot[red,mark=*] table{data/timeB.dat};
	\addplot[green,mark=square] table{data/timeL.dat};
	\end{axis}
	\end{tikzpicture}
	\caption{Execution time comparation graph}
	\label{fig:graph_time}
\end{figure}

\begin{figure}
	\centering
	\begin{tikzpicture}
	\begin{axis}[
	xlabel={Search space ($2^m$)},
	ylabel={Memory usage (byte)},
	legend pos=north west,
	grid style=dashed,
	legend entries={Binary repetition,Binary code,Lookup table},
	]
	\addplot[blue,mark=triangle] table{data/memoryR.dat};
	\addplot[red,mark=*] table{data/memoryB.dat};
	\addplot[green,mark=square] table{data/memoryL.dat};
	\end{axis}
	\end{tikzpicture}
	\caption{Memory usage comparation graph}
	\label{fig:graph_memory}
\end{figure}
